Sequential rank agreement methods for comparison of ranked lists

### 2016-05-26 latex/superranker-manuscript.tex
minor additions

\section{Proof of corollary \ref{cor:consistency}}

>>>>

\section{Proof of Corollary \ref{cor:consistency}}
We have that 	
\begin{align}
  |\widehat{d^\ast_L}(\widehat{q}_L) - d^\ast(q)| &\leq  |\widehat{d^\ast_L}(q)  - d^\ast(q)| + |\widehat{d^\ast_L}(\widehat{q}_L)  - \widehat{d^\ast_L}(q_L)|
\end{align}
The first term is of order $o_P(1)$ by the continuous mapping theorem if a) $|\inf \widehat{\mathcal{L}}_L(q) - \inf  \mathcal{L}(q)| = o_P(1)$ and b) $|1(|\widehat{\mathcal{L}}_L(q)| = 0) - 1(|\mathcal{L}(q)| = 0)| = o_P(1)$ since $1(|\mathcal{L}(q)| > 0) = 1 - 1(|\mathcal{L}(q)| = 0)$. Similarly, the second term is of order $o_P(1)$ by the same reasoning if c) $|\inf \widehat{\mathcal{L}}_L(\widehat{q}_L) - \inf \widehat{\mathcal{L}}_L(q)| = o_P(1)$ and d) $|1(|\widehat{\mathcal{L}}_L(\widehat{q}_L)| = 0) - 1(|\widehat{\mathcal{L}}_L(q)| = 0)| = o_P(1)$.

\begin{align}
\inf \left\{d : \widehat{\textrm{sra}}_L(d) \geq \widehat{q}_L(d)\right\} = \inf \left\{d : \widehat{\textrm{sra}}_L(d) \geq q(d) + o_P(1)\right\}\\
\inf \left\{d : \widehat{\textrm{sra}}_L(d) \geq q(d)\right\}
\end{align}
This completes the proof.
